*cellcount*: an open-source and automated approach to cyanobacteria enumeration

### 2023-02-27 draft_manuscript.Rmd
Small updates to authorship

  - name: Kaytee Pokrzywinski
    affiliation: National Oceanic and Atmospheric Administration, National Centers for Coastal Ocean Science, Beaufort, NC 28516, USA
date: "`r Sys.Date()`"
output: distill::distill_article
---
# Summary

>>>>

  - name: Kaytee Pokrzywinski
    affiliation: National Oceanic and Atmospheric Administration, National Centers for Coastal Ocean Science, Beaufort, NC 28516, USA
    orcid_id: 0000-0003-1523-9930
date: "`r Sys.Date()`"
output: distill::distill_article
---
# Summary
